Attrition in Online Learning: Understanding Persistence and Dropout in Massive Open Online Courses

### 2014-10-16 paper_v1.Rnw
added some research questions and hypotheses

@@

>>>>

TODO: develop

\begin{description}
  \item[RQ1] Why do people who drop out report they drop out?
  \item[RQ2] Who is most likely to drop out in terms of demographics, intentions/motivations, geo location, prior experience with online courses?
  \item[RQ3] What reasons do people from different subgroups (demographic, intention, etc.) report for dropping out?
  \item[RQ4] What proportion of people who dropped out were satisfied with what they got out of the course?
  \item[RQ5] What behaviors do people with different dropout reasons exhibit?
  \item[H1] prior experience -- technical difficulties
  \item[H2] demographics (education) -- course difficulty
\end{description}

@@

TODO: develop

H1: People who report `not enough time' can be split into those who have external constraints and those who have low volition.

H2: people who report external committments (family, school), are more likely to specify the reason than people who have `no time' because they have low volition
